Cluster Difference Imaging Photometric Survey. III. An Open Cluster Spread Across 400\,pc

### 2021-03-10 cluster_paper/ms.tex
update ms

\begin{figure*}[t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f8a.pdf}
			\includegraphics[width=0.5\textwidth]{f8b.pdf}
		}
	%		\includegraphics[width=0.7\textwidth]{f8a.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ 
  {\bf Members of NGC\,2516 exist hundreds of parsecs from the core,
  and up to $\approx$5\kms\ from the core in tangential velocity.} Stars
  that meet both kinematic and rotational membership criteria are shown in
  blue.  Stars for which rotation periods should have been detectable,
  but were not detected, are shown in orange.  Projections are shown in galactic coordinates and
  (projection-corrected) 2D-tangential velocity space.  The histogram
  on the right bins versus 3D separation from the core and
  2D velocity difference. Bins have width 25\,pc
  in position, and 1.0\,km\,s$^{-1}$ in velocity.  {\bf Uncertainties
  in the fraction are taken as the quadrature sum of the rel unc of
  the numerator and denominator (FIXME)}
  \label{fig:physical_x_rotn}
	}
\end{figure*}

>>>>

\begin{figure*}[t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f8a.pdf}
			\includegraphics[width=0.5\textwidth]{f8b.pdf}
		}
	%		\includegraphics[width=0.7\textwidth]{f8a.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ 
  {\bf Members of NGC\,2516 exist hundreds of parsecs from the core,
  and up to $\approx$5\kms\ from the core in tangential velocity.}
  Halo members
  that meet both kinematic and rotational membership criteria are shown in
  blue.  Halo members for which rotation periods should have been detectable,
  but were not detected, are shown in orange.  Projections are shown in galactic coordinates and
  (projection-corrected) 2D-tangential velocity space.  The histogram
  on the right bins versus 3D separation from the core and
  2D velocity difference. Bins have width 25\,pc
  in position, and 1.0\,km\,s$^{-1}$ in velocity.  {\bf Uncertainties
  in the fraction are taken as the quadrature sum of the rel unc of
  the numerator and denominator (FIXME)}
  \label{fig:physical_x_rotn}
	}
\end{figure*}
